An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-29 paper/1.introduction.tex
small fixes

\textcolor{red}{If the BX programs are simple like the running examples, we can transform left associative compositions to right associative. However, this is not always possible. For example, let us consider a BX 'reverse' program, $breverse$. $breverse$ is constructed by application of $bfoldr$ (the actual program is shown in the last part of Section~\ref{sect:minbigul}) and $bsnoc$.
A part of the definition of $bfoldr$, we have $(\product{Replace}{(bfoldr \ bx)}) \circ bx$. In this program, recursion occurs on the left-hand side of composition. Because of priority, it is impossible to transform this program to right associative compositions. At the same time, we can not apply program fusion \cite{Wadler:1988:DTP:80099.80104} to this program because this BX program is dynamically produced depending on the length of the input list. Therefore, it is important to have a fast evaluation method for left associative compositions.}

For achieving this, we introduce two methods that use memoization.
The first method uses memoization simply: ``keeping all intermediate states and using them when they are needed.'' There is no quadratic $get$s in this method, therefore this method improves the runtime of many BX programs. However, a disadvantage of this is the familiar tradeoff for keeping and searching values in a table. Especially, when we use large inputs, the evaluation time will be long. We explain this method in Section~\cite{sect:minbigl_m}.

>>>>

\textcolor{red}{If the BX programs are simple like the running examples, we can transform left associative compositions to right associative. However, this is not always possible. For example, let us consider a BX 'reverse' program, $breverse$. $breverse$ is constructed by application of $bfoldr$ (the actual program is shown in the last part of Section~\ref{sect:minbigul}) and $bsnoc$.
A part of the definition of $bfoldr$, we have $(\product{Replace}{(bfoldr \ bx)}) \circ bx$. In this program, recursion occurs on the left-hand side of composition. Because of priority, it is impossible to transform this program to right associative compositions. At the same time, we can not apply program fusion \cite{Wadler:1988:DTP:80099.80104} to this program because actual program is dynamically produced by recursions depending on the length of the input list. Therefore, it is important to have a fast evaluation method for left associative compositions.}

For fast evaluation for left associative compositions, we introduce two methods that use memoization.
The first method uses memoization simply: ``keeping all intermediate states and using them when they are needed.'' There is no quadratic $get$s in this method, therefore this method improves the runtime of many BX programs. However, a disadvantage of this is the familiar tradeoff for keeping and searching values in a table. Especially, when we use large inputs, the evaluation time will be long. We explain this method in Section~\ref{sect:minbigulm}.
